### 2021-10-22 paper.Rmd
working on results for simulation, using Table

```{r setup, include = FALSE}
library("papaja")
library("anticlust")
library("knitr")
library("dplyr")
library("ggplot2")
library("tidyr")
options(digits = 2)
knitr::opts_chunk$set(message=FALSE, warning = FALSE, echo = FALSE, dev = "cairo_pdf")

@@

First, I investigated how well maximizing the k-plus criterion approximates the ordinary k-means criterion at the same time. Figure 2 illustrates the relative values of $\mathit{SSE}$ that were found when optimizing $\mathit{SSE_{kplus}}$---as compared to the direct optimization of $\mathit{SSE}$. Generally, optimizing $\mathit{SSE_{kplus}}$ yielded an adequate approximation of $\mathit{SSE}$. In particular, for large group sizes, there is virtually no sacrifice in $\mathit{SSE}$ when  $\mathit{SSE_{kplus}}$ is optimized: For $N > 100$, $\mathit{SSE}$ was approximated to more than `r cut_decimals(approx_n100, 4) * 100`% when conducting k-plus anticlustering as compared to k-means anticlustering. In the simulation, the worst approximation was found when the group sizes were smallest: for $N = 24$ and $K = 4$ was approximated to $\mathit{SSE}$ `r approx_n24_k4 * 100`%. Thus, the quality of the approximation depended on the group size: smaller groups led to worse approximations, while in general there was very little in $\mathit{SSE}$, expecially for larger groups.

In a next step, I compared k-means anticlustering, k-plus anticlustering and anticluster editing in their ability to equalize means and standard deviations between groups.

```{r, fig.cap = "Awesome caption", fig.height = 6.5, fig.width = 5}

ldf %>% 
  group_by(method, Objective, N, K) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(Objective %in% c("means", "sd"), method != "random") %>% 
  ggplot(aes(x = N, y = Mean, colour = method)) + 
  geom_line(aes(colour = method), size = .7) + 
  geom_point(aes(colour = method, shape = method)) +
  facet_grid(cols = vars(Objective), rows = vars(K), scales = "free") + 
  theme_apa() +
  theme(
    legend.position = "top",
    legend.title = element_text()
  ) + 
  guides(
    linetype = guide_legend(title = "Method"),
    shape = guide_legend(title = "Method")
  ) +
  theme(
    legend.position = "top",
    legend.title = element_text()
  ) +
  scale_colour_grey(name = "Method")

@@

- k-plus approximates k-means very well, especially for large $N$ (for larger $K$, $N$ schould increase as well)
- k-plus is the best method to optimize similarity with regard to means and standard deviations at the same time

@@

The simulation study indicated that k-plus may show decreased performance for smaller group sizes. Therefore,    this second example application illustrates that k-plus anticlustering may also yield satisfactory results when group are smaller than in the OASIS example. I employ a norming data set of 96 word stimuli that was contributed to the `anticlust` package by Dr. Schaper [@schaper2019metacognitive; @schaper2019metamory; also see @papenberg2020 for a description of the norming data]. After loading the `anticlust` package, the data set can be accessed as follows:

>>>>

```{r setup, include = FALSE}
library("papaja")
library("anticlust")
library("knitr")
library("dplyr")
library("ggplot2")
library("tidyr")
library("prmisc") # remotes::install_github("m-Py/prmisc")
options(digits = 2)
knitr::opts_chunk$set(message=FALSE, warning = FALSE, echo = FALSE, dev = "cairo_pdf")

@@

First, I investigated how well maximizing the k-plus criterion approximates the ordinary k-means criterion at the same time. Figure 2 illustrates the relative values of $\mathit{SSE}$ that were found when optimizing $\mathit{SSE_{kplus}}$---as compared to the direct optimization of $\mathit{SSE}$. Generally, optimizing $\mathit{SSE_{kplus}}$ yielded an adequate approximation of $\mathit{SSE}$. In particular, for large group sizes, there is virtually no sacrifice in $\mathit{SSE}$ when  $\mathit{SSE_{kplus}}$ is optimized: For $N > 100$, $\mathit{SSE}$ was approximated to more than `r cut_decimals(approx_n100, 4) * 100`% when conducting k-plus anticlustering as compared to k-means anticlustering. In the simulation, the worst approximation was found when the group sizes were smallest: for $N = 24$ and $K = 4$ was approximated to $\mathit{SSE}$ `r approx_n24_k4 * 100`%. Thus, the quality of the approximation depended on the group size: smaller groups led to worse approximations, while in general there was very little cost with regard $\mathit{SSE}$ when optimizing $\mathit{SSE_{kplus}}$, expecially for larger groups.

In a next step, I compared k-means anticlustering, k-plus anticlustering and anticluster editing in their ability to equalize means and standard deviations between groups. The results are shown in Table 1.

```{r, fig.cap = "Awesome caption"}

# Recode N into categories so the results can be displayed in a more informative way
ldf <- within(ldf, {
  N_category <- ifelse(N <= 200, "N <= 200", "N > 200")
  N_category <- ifelse(N <= 100, "N <= 100", N_category)
  N_category <- ifelse(N <= 50,  "N <= 50", N_category)
})

ldf$N_category <- ordered(
  ldf$N_category, 
  levels = c("N <= 50", "N <= 100", "N <= 200", "N > 200")
)

# for sorting by method, make it ordered factor:
ldf$method <- ordered(
  ldf$method, 
  levels = c("k-means-exchange", "kplus", "ace-exchange"),
  labels = c("k-means", "k-plus", "anticluster editing")
)

results_table <- ldf %>% 
  group_by(method, Objective, N_category) %>% 
  summarise(Mean = mean(value)) %>% 
  filter(Objective %in% c("means", "sd"), method != "random") %>% 
  pivot_wider(names_from = Objective, values_from = Mean) %>%
  arrange(N_category, method)

# enforce two decimals
results_table$means <- force_decimals(results_table$means, 2)
results_table$sd <- force_decimals(results_table$sd, 2)

# Generate table
footnote <- "$\\Delta M$ and $\\Delta \\mathit{SD}$ quantify how strongly means and standard deviations differed between anticlusters. Table cells contain the average objectives across simulation runs, split by $N$."

results_table$N_category <- NULL

colnames <- c("", "$\\Delta M$", "$\\Delta \\mathit{SD}$")
colnames(results_table) <- colnames

apa_table(
  results_table, 
  caption = "Results of the simulation study.", 
  note = footnote, 
  escape = FALSE,
  stub_indents = list("\\textbf{$\\textit{N} \\leq 50$}" = 1:3,
                      "\\textbf{$50 <\\textit{N} \\leq 100$}" = 4:6,
                      "\\textbf{$100 <\\textit{N} \\leq 200$}" = 7:9,
                      "\\textbf{$\\textit{N} > 200$}" = 10:12),
  span_text_columns = TRUE
)

@@

- k-plus is the best method to optimize similarity with regard to means and standard deviations at the same time

@@

The simulation study indicated that k-plus may show decreased performance for smaller group sizes. Therefore, a second application illustrates that k-plus anticlustering may yield satisfactory results in practice, when group are smaller. I make use of a norming data set of 96 word stimuli that was contributed to the `anticlust` package by Dr. Schaper [@schaper2019metacognitive; @schaper2019metamory; also see @papenberg2020 for a description of the norming data]. After loading the `anticlust` package, the data set can be accessed as follows:
